Hybrid platforms and bargaining

### 2023-06-16 src/presentation/io_day.qmd
Even more last-minute changes

::: {.fragment fragment-index=2}
 - The platform likes being hybrid
   - It's profits increase in $N_P$
:::
::: {.fragment fragment-index=4}
 - It depends™ for the fringe
   - It's profits increase if and only if platform and fringe products are complements:
     $$ \scriptsize \frac{\partial f^2}{N_P N_F} > 0 $$
:::

@@

::: {.fragment fragment-index=3}
 - If $\frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0$, hybrid mode reduces fringe entry

@@

::: {.incremental}
 - Equilibrium aggregate and total profits are decreasing in $N_P$
 $$
 \frac{\partial A^*}{\partial N_P} < 0
 $$
   - Platform profits are increasing in $N_P$, though
 - **Consumer surplus** is also **decreasing** in $N_P$
 $$
 \frac{\partial CS^*}{\partial N_P} < 0
 $$
:::

@@

::: {.fragment}
 - **Tractable model** of hybrid platforms in which **bargaining** plays a key role
   - Applicable to other settings, too (e.g. vertical markets, franchises)
:::
::: {.fragment}
 - Highlight an important aspect if hybrid platforms
   - **Hybrid mode increases bargaining power** against entrants
   - This can have **negative welfare consequences**
:::
::: {.fragment}
 - Policy implications for such markets
   - Amazon operating in hybrid mode
   - Microsoft acquiring Activision/Blizzard for $68bn
:::

>>>>

::: {.fragment fragment-index=2}
 - The platform likes being hybrid
   - It's profits increase in $N_P$
:::
::: {.fragment fragment-index=4}
 - It depends™ for the fringe
   - It's profits decrease if platform and fringe products are substitutes:
     $$ \scriptsize \frac{\partial f^2}{N_P N_F} < 0 $$
:::

@@

::: {.fragment fragment-index=3}
 - If $\frac{\partial^2 f(N_P, N_F)}{\partial N_P \partial N_F} < 0$, hybrid mode reduces fringe entry

@@

::: {.incremental}
 - Equilibrium aggregate and total profits are decreasing in $N_P$
 $$
 \frac{\partial A^*}{\partial N_P} < 0
 $$
   - Platform profits are increasing in $N_P$, though
 - **Consumer surplus** is also **decreasing** in $N_P$
 $$
 CS^* \propto \log(A^*) \implies \frac{\partial CS^*}{\partial N_P} < 0
 $$
:::

@@

::: {.fragment}
 - **Tractable model** of hybrid platforms in which **bargaining** plays a key role
   - Applicable to other settings, too (e.g. vertical markets, franchises)
:::
::: {.fragment}
 - Highlight an important aspect of hybrid platforms
   - **Hybrid mode increases bargaining power** against entrants
   - This can have **negative welfare consequences**
:::
::: {.fragment}
 - Policy implications for such markets
   - Amazon operating in hybrid mode
   - Microsoft acquiring Activision/Blizzard for $68bn
:::
